Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2019-03-04 paper/paper.tex
cleaned up citations

We first performed a multiplex PCR reaction on 1 ng of the full-length 10X cDNA using a 3' primer complementary to the common 10X adaptor, and a multiplex mix of eight 5' primers, one specific for the mRNAs from each of the eight viral gene segments (although some viral segments produce multiple splice forms, all mRNAs from a given segment share the same 5' end).
The sequences of these primers are in \SUPPFILE{primer_sequences}.
A major concern during these PCRs is strand exchange (see \SUPPFIG{StrandExchange}) which would scramble the cell barcodes and mutations on viral cDNAs.
To reduce strand-exchange and hopefully obtain more even PCR amplification across segments, we performed emulsion PCRs using the Micellula DNA Emulsion Kit (Roboklon).
Emulsion PCR involves encapsidating DNA template molecules in a reverse-phase emulsion, with each template positive droplet serving as a microreactor.
This process physically separates disparate template molecules, preventing strand exchange and allowing each molecule to be amplified to exhaustion of its droplet's reagents without competing with the broader pool of PCR-amenable molecules~\cite{Boers:2015emulsion}.
We performed the PCRs using Kapa HiFi Hotstart ReadyMix, supplementing the reactions with additional BSA to a final concentration of 0.1 mg/ml and using a volume 100$\mu$l .
Both the common 3' primer and the multiplex mix of eight 5' primers were added to a final concentration of 0.5$\mu$M.
We performed 30 cycles of PCR, using an extension time of 2 minutes 15 seconds at 67$^{\circ}$C, and a melting temperature of 95$^{\circ}$C.
This melting temperature is lower than the standard 98$^{\circ}$C melting step suggested by the manufacturer for Kapa HiFi because we wanted to avoid collapse of emulsion integrity at high temperature.
We performed 30 cycles in order to saturate the reagents in each emulsion---unlike for open PCR reactions, the physical occlusion of amplified material in emulsion PCR reduces artifacts at high cycle numbers.

>>>>

We first performed a multiplex PCR reaction on 1 ng of the full-length 10X cDNA using a 3' primer complementary to the common 10X adaptor, and a multiplex mix of eight 5' primers, one specific for the mRNAs from each of the eight viral gene segments (although some viral segments produce multiple splice forms, all mRNAs from a given segment share the same 5' end).
The sequences of these primers are in \SUPPFILE{primer_sequences}.
A major concern during these PCRs is strand exchange (see \SUPPFIG{StrandExchange}) which would scramble the cell barcodes and mutations on viral cDNAs.
To reduce strand-exchange and hopefully obtain more even PCR amplification across segments, we performed emulsion PCRs using the Micellula DNA Emulsion Kit (Roboklon).
Emulsion PCR involves encapsidating DNA template molecules in a reverse-phase emulsion, with each template positive droplet serving as a microreactor.
This process physically separates disparate template molecules, preventing strand exchange and allowing each molecule to be amplified to exhaustion of its droplet's reagents without competing with the broader pool of PCR-amenable molecules~\cite{boers2015micelle}.
We performed the PCRs using Kapa HiFi Hotstart ReadyMix, supplementing the reactions with additional BSA to a final concentration of 0.1 mg/ml and using a volume 100$\mu$l .
Both the common 3' primer and the multiplex mix of eight 5' primers were added to a final concentration of 0.5$\mu$M.
We performed 30 cycles of PCR, using an extension time of 2 minutes 15 seconds at 67$^{\circ}$C, and a melting temperature of 95$^{\circ}$C.
This melting temperature is lower than the standard 98$^{\circ}$C melting step suggested by the manufacturer for Kapa HiFi because we wanted to avoid collapse of emulsion integrity at high temperature.
We performed 30 cycles in order to saturate the reagents in each emulsion---unlike for open PCR reactions, the physical occlusion of amplified material in emulsion PCR reduces artifacts at high cycle numbers.
